### 2017-02-03 introduction.tex
Minor revisions to Introduction and Conclusion

The IMF interacts with the Earth's own magnetic field, and this interaction creates the magnetosphere.  Without the IMF, the magnetosphere would be approximately in a dipole shape, but dynamic pressure from the solar wind causes the Sun-facing side to be compressed to 6--10 Earth radii and the opposite side to be stretched into an extended tail (hundreds of Earth radii).  Because the solar wind is typically a supersonic flow, a bow shock forms on the dayside of the magnetosphere.  The heated and compressed solar wind plasma created by the bow shock is known as the magnetosheath, the red region in Figure \ref{fig:ste}.  The magnetopause, black dashed line, is the actual boundary between solar wind plasma in the magnetosheath and magnetospheric plasma.  Magnetic field lines that are part of the closed magnetosphere are shown in grey in Figure \ref{fig:ste}.  However, the magnetosphere is not fully closed.  At the magnetopause, magnetic reconnection can occur between the IMF and the Earth's magnetic field creating open field lines, light blue in Figure \ref{fig:ste}.  This reconnection occurs on last closed field line intersecting the magnetopause (highlighted in yellow in Figure \ref{fig:ste}).  Magnetic field lines originating from the Earth are then directly connected to the Sun through the solar wind, which consequently allows highly energized solar particles to enter the magnetosphere.  Open field lines tend to occur around the Earth's polar caps, making these regions particularly interesting to study due to very complex behavior and coupled interactions between the Earth and the Sun.

@@

Because the concentrations of ions and neutral particles changes with altitude, each of these regions have distinct plasma physical properties that make them unique.  The main issue is whether the large-scale motion of a particle is controlled more by the magnetic field (the particle is magnetized) or by collisions with other particles (the particle is collisional).  This can be determined by comparing the collision frequency, \(\nu_\alpha\), to the gyrofrequency, \(\Omega_\alpha\), of a particular species, where \(\alpha\) refers to either electrons, \(e\), or ions, \(i\).  If \(\Omega_\alpha \gg \nu_\alpha\), the particle completes many gyrations between each collision, so its motion is determined mostly by the magnetic field and it is considered to be magnetized.  If \(\nu_\alpha \gg \Omega_\alpha\), the particle collides with other particles much more often than it completes a gyration, so it is considered collisional.  The gyrofrequency is dependent on the mass and charge of the particle and the strength of the magnetic field, \(\Omega_\alpha = q_\alpha B/m_\alpha\), so it is roughly constant throughout the ionosphere because the magnetic field strength does not change much throughout these altitudes.  The collision frequency depends on the density of a species relative to the density of all other species in the plasma and can be calculated from a series of standard expressions \citep{Schunk1980,Schunk2009}.  In the \(E\) region, \(\Omega_e \gg \nu_e\), so electrons are magnetized.  However, the motion of ions is dominated by collisions between ions and neutrals (\(\nu_i > \Omega_i\)), so ions in the \(E\) region are considered collisional.  In the \(F\) region where the neutral density is much lower, both ions and electrons are magnetized, \(\Omega_\alpha \gg \nu_\alpha\).  These differences in how charged particles move impact the conductivity and plasma waves development, which is further discussed in Section \ref{sec:lit_instabilities}.

@@

Small-scale structuring is generally considered to be all irregularities less than 100 m \citep{Kelley2009}.  Although small-scale irregularities are not responsible for scintillation that directly impact GPS/GNSS performance, they can be the easiest to study because of extensive datasets collected with a large number of ionospheric radars around the world that have been in operation for many decades (discussed further in Section \ref{sec:superdarn}).  Because electrons move far more easily along magnetic field lines than across them, density perturbations tend to be aligned with the magnetic field and are often known as field-aligned irregularities (FAI), Figure \ref{fig:polarirreg}d.  The irregularity classifications presented here are rough categories only and a high degree of coupling occurs between different scales, which makes plasma structures of all scales (large, intermediate, and small) important for plasma structuring processes.  For instance, large-scale structures such as polar patches may very well have internal intermediate- and/or small-scale structuring.  A turbulent cascade is often assumed to connect these different scales, but because various instruments or techniques usually only observe structuring on a particular scale, it is difficult to find direct evidence of this or how exactly it occurs \citep{Kintner1985,Tsunoda1985}.  A description of some of the particular instruments and models that are used in this thesis follows.

@@

When the radar transmits continuously, backscatter will be received, but because it is impossible to know when that signal was transmitted, the difference in time between transmission and receiving cannot be used to calculate how far away the backscatter volume is.  Conversely, if the radar only transmits a pulse of a certain length of a certain length and then ``listens'' for its return, the time between transmission and return is known and the distance the pulse traveled can be calculated and therefore the location of the backscattering volume can be found \citep{Farley1972,Greenwald1983}.  However, using this simple single-pulse method, another pulse cannot be transmitted until the first pulse returns, limiting the temporal resolution that can be achieved.  This can be improved by using a multi-pulse scheme, which will be discussed below \citep{Farley1972,Greenwald1983,Greenwald1985}.

A short time between pulse returns is necessary to allow Doppler velocities to be calculated, particularly at long ranges.  The maximum Doppler shifted frequency that can be observed by a radar is the Nyquist frequency, \(f_n\), which is equivalent to half the sampling frequency, \(f_s\),
\begin{equation}	
	\label{eqn:nyquist}
	f_n = \frac{f_s}{2}.
\end{equation}
Radars operating in a single-pulse mode must have a very low sampling frequency, as described above, particularly at long ranges where the pulse must travel a long distance.  This severely limits the Doppler shift that can be measured, which places an upper limit on the LoS velocity that can be calculated with this technique.  For an ionospheric radar observing a structure 2000 km away, it would take about 13 ms for a signal traveling at the speed of light to travel to the structure and back to the radar, which corresponds to a sampling frequency of \(f_s = 75\) Hz.  The Nyquist frequency is then \(f_n = 37.5\) Hz, which corresponds to a maximum measurable Doppler velocity of \(\sim550\) m/s.  Flows in the ionosphere have been known to exceed 1000--2000 m/s, so single-pulse sampling is insufficient for these purposes.

@@

The first observations of the ionosphere by CSRs were made in the 1930s \citep{Eckersley1937,Harang1938}.  Over the next several decades, numerous ground-based radars have been used to advance our understanding of the ionosphere and radio aurora \citep{Hultqvist1964,Leadabrand1965,Unwin1972,Sahr1996}.  In the 1970s and 1980s, the Scandanavian Twin Auroral Radar Experiment (STARE) produced the first continuous large data-set, similar to how modern CSR systems are run.  STARE consisted of two very high frequency (VHF) radars with overlapping fields-of-view (FoV) that were designed to measure FAIs in the \(E\) region of the ionosphere \citep{Greenwald1997}.  The advantage of two radars with overlapping FoVs was the ability to observe the same structures from two different directions.  Because each radar can only measure the LoS velocity of a structure, two simultaneous observations from different directions allows two different velocity vector components to be found, and hence the total velocity vector can be calculated.  This technique is still commonly used with CSR system.

@@

Although the IRI model is very useful for providing background plasma density conditions where no instruments are available to make measurements, it is important to bear in mind that it is a model and therefore only represents the average conditions.  Although it is fairly accurate at mid-latitudes \citep{Coisson2006,Bilitza2012}, it does not necessarily represent variations within the polar cap well \citep{Themens2014,Makarevich2015b}.  In particular, the height of the \(F\)-region peak tends to be underestimated in daytime and the bottomside thickness does not show realistic seasonal and diurnal variations \citep{Themens2014}.

@@

\subsection{Polar Patch Formation}
\label{sec:lit_patches}
Large-scale structuring in the polar cap can take a variety of forms, Section \ref{sec:polar_structure}, but here the focus is on large regions of enhanced plasma density known as polar patches  \citep[e.g.][]{Weber1984,Weber1986,Buchau1983,Buchau1985}.  One of the primary interests of this thesis is the relationships between large-scale plasma structures ans small-scale irregularity formation.  This structuring has long been observed around polar patches \citep{Weber1984,Milan2002b,Moen2012}.  Although small-scale structures have also been observed around sun-aligned arcs \citep[e.g.][]{Koustov2012}, these structures also tend to be more complicated and often are surrounded by intense shears and electric fields \citep{Safargaleev2000,Aikio2002,Kozlovsky2007}.  Additionally, polar patches occur relatively frequently, providing a good opportunity to study irregularity coupling at different scales \citep{Rodger1996}.  In theory, many of the results presented in this work pertaining to the strong gradients on the edges of patches could also easily be applied to the edges of polar holes, but to date, far less attention has been paid to polar holes in the literature, making it challenging to accurately put observations in context \citep{Makarevich2015b}.

The first observations of polar patches were made in the 1960s by \citet{Hill1963}.  They can range in size from 100 km up to 1500 km and can have peak densities as much as eight times that of the background ionospheric plasma \citep{Weber1986,Hosokawa2014}.  Polar patches are known to emerge on the dayside and then propagate with the background plasma convection across the polar cap to the nightside, where they either disintegrate or recombine with enhanced-density plasma in the auroral oval \citep{Weber1985,Weber1986}.

@@

\subsection{Theory of Plasma Instabilities}
\label{sec:lit_instabilities}
Plasma structuring, especially at smaller scales, is often discussed in terms of the growth or damping of plasma waves, or instabilities.  As discussed previously in Section \ref{sec:ionosphere_regions}, the plasma characteristics change with altitude in the ionosphere, which causes a variety of different instability mechanisms to be operational depending on the region considered.  The Farley-Buneman instability (FBI), or the modified two-stream instability tends to be a major factor in the \(E\) region where ion inertial effects are strong \citep{Farley1963,Buneman1963}.  Also operational in the \(E\) region but more dominant at higher altitudes is the gradient-drift instability (GDI) \citep{Simon1963,Hoh1963,Linson1970}.  If a wave propagation vector has a component along the magnetic field line, the current-convective instability (CCI) can be operational even if GDI is not \citep{Hoh1960,Ossakow1979,Chaturvedi1981}.  Additional instability mechanisms emerge if shears are considered, when \(\nabla E \neq 0\), such as the Kelvin-Helmholtz instability (KHI) \citep{Kintner1977,DAngelo1965}.

@@

Recently, a new expression has been introduced that considers any arbitrary wavevector, density gradient, and altitude within the ionosphere, which allows three electrostatic instabilities, FBI, GDI, and CCI, to be considered within a single dispersion relation \citep{Makarevich2016a}
\begin{equation}
	\label{eqn:gdi_Mak16}
	(H_i-H_e)\omega = (H_i\vec{V}_{e0}-H_e\vec{V}_{i0})\cdot\vec{k}+(C_i-C_e)H_eH_i.
\end{equation}
Here, \(\vec{k}\) is the wavevector, \(\omega\) is the wave frequency, and \(\vec{V}_{\alpha 0}\) is the background velocity of species \(\alpha\).  All other quantities in Equation \ref{eqn:gdi_Mak16} are not standard and described below.
\begin{equation}
\begin{split}
	H_\alpha = S_\alpha F_\alpha + D_\alpha^{-1} F_\parallel \quad\quad\quad\quad&\quad\quad\quad\quad 
	C_\alpha = \frac{T_\alpha}{m_\alpha \Omega_\alpha} \\
	F_\alpha = i k_\perp^2 D_\alpha + \vec{G}\cdot\vec{k}_\perp D_\alpha + \vec{G}\cdot\vec{k}\times\uvec{b} \quad\quad&\quad\quad\quad\quad
	F_\parallel = i k_\parallel^2 + \vec{G}\cdot\vec{k}_\parallel \\
	S_\alpha = \frac{1}{1+D_\alpha^2} \quad\quad\quad\quad\quad\quad&\quad
	D_\alpha = -\frac{i}{\Omega_\alpha}(\omega-\vec{k}\cdot{V}_{\alpha 0})+r_\alpha
\end{split}
\end{equation}
Throughout this thesis, \(T_\alpha\) and \(m_\alpha\) refer to the temperature and mass of species \(\alpha\), respectively.  The unit vector \(\uvec{b}\) is in the direction of the magnetic field \(\vec{B}\) and \(\vec{k}_\perp\) is the component of the wavevector \(\vec{k}\) perpendicular to the magnetic field while \(\vec{k}_\parallel\) is the component parallel to it.  The gradient strength, \(\vec{G}\), is defined by \(\vec{G} = \nabla n/n\) such that the magnitude of the gradient strength is equivalent to the inverse gradient scale length, \(G = L^{-1}\).  The quantity \(r_\alpha\) is the ratio of the collision frequency to the gyrofrequency of a particular species, given by \(r_\alpha = \nu_\alpha/\Omega_\alpha\).

>>>>

The IMF interacts with the Earth's own magnetic field, and this interaction creates the magnetosphere.  Without the IMF, the magnetosphere would be approximately in a dipole shape, but dynamic pressure from the solar wind causes the Sun-facing side to be compressed to 6--10 Earth radii and the opposite side to be stretched into an extended tail (hundreds of Earth radii).  Because the solar wind is typically a supersonic flow, a bow shock forms on the dayside of the magnetosphere.  The heated and compressed solar wind plasma created by the bow shock is known as the magnetosheath, the red region in Figure \ref{fig:ste}.  The magnetopause, black dashed line, is the actual boundary between solar wind plasma in the magnetosheath and magnetospheric plasma.  Magnetic field lines that are part of the closed magnetosphere are shown in grey in Figure \ref{fig:ste}.  However, the magnetosphere is not fully closed.  At the magnetopause, magnetic reconnection can occur between the IMF and the Earth's magnetic field creating open field lines, light blue in Figure \ref{fig:ste}.  This reconnection occurs on last closed field line intersecting the magnetopause (highlighted in orange in Figure \ref{fig:ste}).  Magnetic field lines originating from the Earth are then directly connected to the Sun through the solar wind, which consequently allows highly energized solar particles to enter the magnetosphere.  Open field lines tend to occur around the Earth's polar caps, making these regions particularly interesting to study due to very complex behavior and coupled interactions between the Earth and the Sun.

@@

Because the concentrations of ions and neutral particles changes with altitude, each of these regions have distinct plasma physical properties that make them unique.  The main issue is whether the large-scale motion of a particle is controlled more by the magnetic field (the particle is magnetized) or by collisions with other particles (the particle is collisional).  This can be determined by comparing the collision frequency, \(\nu_\alpha\), to the gyrofrequency, \(\Omega_\alpha\), of a particular species, where \(\alpha\) refers to either electrons, \(e\), or ions, \(i\).  If \(\Omega_\alpha \gg \nu_\alpha\), the particle completes many gyrations between each collision, so its motion is determined mostly by the magnetic field and it is considered to be magnetized.  If \(\nu_\alpha \gg \Omega_\alpha\), the particle collides with other particles much more often than it completes a gyration, so it is considered collisional.  The gyrofrequency is dependent on the mass (\(m_\alpha\)) and charge of the particle (\(q_\alpha\)) and the strength of the magnetic field (\(B\)), \(\Omega_\alpha = q_\alpha B/m_\alpha\), so it is roughly constant throughout the ionosphere because the magnetic field strength does not change much throughout these altitudes.  The collision frequency depends on the density of a species relative to the density of all other species in the plasma and can be calculated from a series of standard expressions \citep{Schunk1980,Schunk2009}.  In the \(E\) region, \(\Omega_e \gg \nu_e\), so electrons are magnetized.  However, the motion of ions is dominated by collisions between ions and neutrals (\(\nu_i > \Omega_i\)), so ions in the \(E\) region are considered collisional.  In the \(F\) region where the neutral density is much lower, both ions and electrons are magnetized, \(\Omega_\alpha \gg \nu_\alpha\).  These differences in how charged particles move impact the conductivity and plasma waves development, which is further discussed in Section \ref{sec:lit_instabilities}.

@@

Small-scale structuring is generally considered to be all irregularities less than 100 m \citep{Kelley2009}.  Although small-scale irregularities are not responsible for scintillation that directly impacts GPS/GNSS performance, they can be the easiest to study because of extensive datasets collected with a large number of ionospheric radars around the world that have been in operation for many decades (discussed further in Section \ref{sec:superdarn}).  Because electrons move far more easily along magnetic field lines than across them, density perturbations tend to be aligned with the magnetic field and are often known as field-aligned irregularities (FAI), Figure \ref{fig:polarirreg}d.  The irregularity classifications presented here are rough categories only and a high degree of coupling occurs between different scales, which makes plasma structures of all scales (large, intermediate, and small) important for plasma structuring processes.  For instance, large-scale structures such as polar patches may very well have internal intermediate- and/or small-scale structuring.  A turbulent cascade is often assumed to connect these different scales, but because various instruments or techniques usually only observe structuring on a particular scale, it is difficult to find direct evidence of this or how exactly it occurs \citep{Kintner1985,Tsunoda1985}.  A description of some of the particular instruments and models that are used in this thesis follows.

@@

When the radar transmits continuously, backscatter will be received, but because it is impossible to know when that signal was transmitted, the difference in time between transmission and receiving cannot be used to calculate how far away the backscatter volume is.  Conversely, if the radar only transmits a pulse of a certain length of a certain length and then ``listens'' for its return, the time between transmission and return is known and the distance the pulse traveled can be calculated and therefore the location of the backscattering volume can be found \citep{Farley1972,Greenwald1983}.  However, using this simple single-pulse method, another pulse cannot be transmitted until the first pulse returns, limiting the temporal resolution that can be achieved.  This can be improved by using a multi-pulse scheme, which is further discussed below \citep{Farley1972,Greenwald1983,Greenwald1985}.

A short time between pulse returns is necessary to allow Doppler velocities to be calculated, particularly at long ranges.  The maximum Doppler shifted frequency that can be observed by a radar is the Nyquist frequency, \(f_n\), which is equivalent to half the sampling frequency, \(f_s\),
\begin{equation}	
	\label{eqn:nyquist}
	f_n = \frac{f_s}{2}.
\end{equation}
Radars operating in a single-pulse mode must have a very low sampling frequency, as described above, particularly at long ranges where the pulse must travel a long distance.  This severely limits the Doppler shift that can be measured, which places an upper limit on the LoS velocity that can be calculated with this technique.  For an ionospheric radar observing a structure 2000 km away, it would take about 13 ms for a signal traveling at the speed of light to travel to the structure and back to the radar, which corresponds to a sampling frequency of \(f_s = 75\) Hz.  The Nyquist frequency is then \(f_n = 37.5\) Hz, which corresponds to a maximum measurable Doppler velocity of \(\sim550\) m/s.  Flows in the ionosphere are known to exceed 1000--2000 m/s, so single-pulse sampling is insufficient for these purposes.

@@

The first observations of the ionosphere by CSRs were made in the 1930s \citep{Eckersley1937,Harang1938}.  Over the next several decades, numerous ground-based radars have been used to advance our understanding of the ionosphere  \citep{Hultqvist1964,Leadabrand1965,Unwin1972,Sahr1996}.  In the 1970s and 1980s, the Scandanavian Twin Auroral Radar Experiment (STARE) produced the first continuous large data-set, similar to how modern CSR systems are run.  STARE consisted of two very high frequency (VHF) radars with overlapping FoVs that were designed to measure FAIs in the \(E\) region of the ionosphere \citep{Greenwald1997}.  The advantage of two radars with overlapping FoVs was the ability to observe the same structures from two different directions.  Because each radar can only measure the LoS velocity of a structure, two simultaneous observations from different directions allows two different velocity vector components to be found, and hence the total velocity vector can be calculated.  This technique is still commonly used with CSR system.

@@

Although the IRI model is very useful for providing background plasma density conditions where no instruments are available to make measurements, it is important to bear in mind that it is a model and therefore only represents the average conditions.  Although it is fairly accurate at mid-latitudes \citep{Coisson2006,Bilitza2012}, it does not necessarily represent well variations within the polar cap \citep{Themens2014,Makarevich2015b}.  In particular, the height of the \(F\)-region peak tends to be underestimated in daytime and the bottomside thickness does not show realistic seasonal and diurnal variations \citep{Themens2014}.

@@

\subsection{Polar Patch Formation}
\label{sec:lit_patches}
Large-scale structuring in the polar cap can take a variety of forms, Section \ref{sec:polar_structure}, but here the focus is on large regions of enhanced plasma density known as polar patches  \citep[e.g.][]{Weber1984,Weber1986,Buchau1983,Buchau1985}.  One of the primary interests of this thesis is the relationships between large-scale plasma structures and small-scale irregularity formation.  This structuring has long been observed around polar patches \citep{Weber1984,Milan2002b,Moen2012}.  Although small-scale structures have also been observed around sun-aligned arcs \citep[e.g.][]{Koustov2012}, these structures also tend to be more complicated and often are surrounded by intense shears and electric fields \citep{Safargaleev2000,Aikio2002,Kozlovsky2007}.  Additionally, polar patches occur relatively frequently, providing a good opportunity to study irregularity coupling at different scales \citep{Rodger1996}.  In theory, many of the results presented in this work pertaining to the strong gradients on the edges of patches could also easily be applied to the edges of polar holes, but to date, far less attention has been paid to polar holes in the literature, making it challenging to accurately put observations in context \citep{Makarevich2015b}.

The first observations of polar patches were made in the 1960s by \citet{Hill1963}.  Polar patches can range in size from 100 km up to 1500 km and can have peak densities as much as eight times that of the background ionospheric plasma \citep{Weber1986,Hosokawa2014}.  Polar patches are known to emerge on the dayside and then propagate with the background plasma convection across the polar cap to the nightside, where they either disintegrate or recombine with enhanced-density plasma in the auroral oval \citep{Weber1985,Weber1986}.

@@

\subsection{Theory of Plasma Instabilities}
\label{sec:lit_instabilities}
Plasma structuring, especially at smaller scales, is often discussed in terms of the growth or damping of plasma waves, or instabilities.  As discussed previously in Section \ref{sec:ionosphere_regions}, the plasma characteristics change with altitude in the ionosphere, which causes a variety of different instability mechanisms to be operational depending on the region considered.  The Farley-Buneman instability (FBI), or the modified two-stream instability tends to be a major factor in the \(E\) region where ion inertial effects are strong \citep{Farley1963,Buneman1963}.  Also operational in the \(E\) region but more dominant at higher, \(F\)-region altitudes is the gradient-drift instability (GDI) \citep{Simon1963,Hoh1963,Linson1970}.  If a wave propagation vector has a component along the magnetic field line, the current-convective instability (CCI) can be operational even if GDI is not \citep{Hoh1960,Ossakow1979,Chaturvedi1981}.  Additional instability mechanisms emerge if shears are considered, when \(\nabla E \neq 0\), such as the Kelvin-Helmholtz instability (KHI) \citep{Kintner1977,DAngelo1965}.

@@

Recently, a new expression has been introduced that considers any arbitrary wavevector, density gradient, and altitude within the ionosphere, which allows three electrostatic instabilities, FBI, GDI, and CCI, to be considered within a single dispersion relation \citep{Makarevich2016a}
\begin{equation}
	\label{eqn:gdi_Mak16}
	(H_i-H_e)\omega = (H_i\vec{V}_{e0}-H_e\vec{V}_{i0})\cdot\vec{k}+(C_i-C_e)H_eH_i.
\end{equation}
Here, \(\vec{k}\) is the wavevector, \(\omega\) is the wave frequency, and \(\vec{V}_{\alpha 0}\) is the background velocity of species \(\alpha\).  All other quantities in Equation \ref{eqn:gdi_Mak16} are not standard and described below.
\begin{equation}
\begin{split}
	H_\alpha = S_\alpha F_\alpha + D_\alpha^{-1} F_\parallel \quad\quad\quad\quad&\quad\quad\quad\quad 
	C_\alpha = \frac{T_\alpha}{m_\alpha \Omega_\alpha} \\
	F_\alpha = i k_\perp^2 D_\alpha + \vec{G}\cdot\vec{k}_\perp D_\alpha + \vec{G}\cdot\vec{k}\times\uvec{b} \quad\quad&\quad\quad\quad\quad
	F_\parallel = i k_\parallel^2 + \vec{G}\cdot\vec{k}_\parallel \\
	S_\alpha = \frac{1}{1+D_\alpha^2} \quad\quad\quad\quad\quad\quad&\quad
	D_\alpha = -\frac{i}{\Omega_\alpha}(\omega-\vec{k}\cdot\vec{V}_{\alpha 0})+r_\alpha
\end{split}
\end{equation}
Throughout this thesis, \(T_\alpha\) refer to the temperature of species \(\alpha\).  The unit vector \(\uvec{b}\) is in the direction of the magnetic field \(\vec{B}\) and \(\vec{k}_\perp\) is the component of the wavevector \(\vec{k}\) perpendicular to the magnetic field while \(\vec{k}_\parallel\) is the component parallel to it.  The gradient strength, \(\vec{G}\), is defined by \(\vec{G} = \nabla n/n\) such that the magnitude of the gradient strength is equivalent to the inverse gradient scale length, \(G = L^{-1}\).  The quantity \(r_\alpha\) is the ratio of the collision frequency to the gyrofrequency of a particular species, given by \(r_\alpha = \nu_\alpha/\Omega_\alpha\).
